---
output: pdf_document
---

```{r global_options, include=FALSE}
rm(list=ls()) ### To clear namespace
library(knitr)
opts_chunk$set(eval=TRUE, include = TRUE, echo = TRUE,
               warning=FALSE, message=FALSE,
               fig.width=8, fig.height=6)
```


# Development, stress response and recovery.

```{r}
require(dplyr)
require(tidyr)
require(ggplot2)
require(stats)



mytheme <- theme_bw() + theme(
  legend.title  = element_text( size=6),
  #  legend.position = "bottom",
  #	legend.direction = "horizontal",
  legend.key = element_blank(),
  legend.text  = element_text( size=6),
  panel.background = element_blank(),
  panel.grid = element_blank(),
  text = element_text( family="Helvetica", size=9),
  panel.border = element_rect( colour = "black", size=1),
  axis.ticks = element_line(size = 1.)
)


```



```{r}
### IMPORT AND NORMALIZE WITHIN ARRAYS ###

filedata = "../../../Data/MicroArrays/projection_alldata.Rdata"

load(filedata)

```


#Parental lines


Plotting heat-shock axis vs time

```{r}
p <- ggplot(  ) + mytheme +   geom_point(
  data = projection_all %>% filter( line == "PL" , agebeginshock == 46 , include == "in" )   ,
  aes(
    x = as.numeric(abstime),
    y = hsprojection,
    colour = as.factor(experimentype),
    shape = as.factor(genotype)
  ) ,
 size = 5, alpha = 0.5 ) +
  stat_smooth( data =  projection_all %>% filter( line == "PL" , agebeginshock == 46 , include == "in" ) ,
               aes(     x = as.numeric(abstime),
                      y = hsprojection,
                      colour = as.factor(experimentype) ),
               se = FALSE , linetype = 2 ) +
     scale_x_continuous( name = "time [hours]"  ) +
   scale_y_continuous( name = "Projection on heat-shock response axis [arbitrary units]"  ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)

```

Plotting development-axis vs time

```{r}
p <- ggplot(  projection_all %>% filter( line == "PL" , agebeginshock == 46   , include == "in")  ) + mytheme +
  aes(
    x = as.numeric(abstime),
    y = devprojection,
    colour = as.factor(experimentype),
    shape = as.factor(genotype)
  ) +# stat_smooth( se = FALSE , linetype = 2 ) +
  geom_point( size = 5, alpha = 0.5 ) +
   scale_x_continuous( name = "time [hours]"  ) +
   scale_y_continuous( name = "Projection on heat-shock response axis [arbitrary units]"  ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)

```

#Considering RILs and NILs

```{r}
p <- ggplot( ) + mytheme +
  geom_point( data = projection_all %>% filter( line == "PL" , agebeginshock == 46 , include == "in" ),
              aes( 
                    x = as.numeric(abstime),
                    y = hsprojection,
                    colour = as.factor(experimentype)
                ), alpha = 0.4, size = 5 )+
    geom_point( data = projection_all %>% filter( line != "PL" , agebeginshock == 46 , include == "in" ),
              aes( 
                    x = as.numeric(abstime),
                    y = hsprojection,
                    colour = as.factor(experimentype)
                ), shape = 21, alpha = 1, size = 3 )+
   scale_x_continuous( name = "time [hours]"  ) +
   scale_y_continuous( name = "Projection on heat-shock response axis [arbitrary units]"  ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 
  

show(p)

```

```{r}
p <- ggplot( ) + mytheme +
  geom_point( data = projection_all %>% filter( line == "PL" , agebeginshock == 46 , include == "in", experimentype == "Dev" ),
              aes( 
                    x = as.numeric(abstime),
                    y = -devprojection,
                    colour = as.factor(genotype),
                    shape = as.factor(genotype)
                ), alpha = 0.4, size = 8 )+
    geom_point( data = projection_all %>% filter( line == "RIL" , agebeginshock == 46 , include == "in", experimentype == "Dev" ),
              aes( 
                    x = as.numeric(abstime),
                    y = -devprojection,
                    colour = as.factor(line)
                ), shape = 21, alpha = 1, size = 3 )+
   scale_x_continuous( name = "time [hours]"  ) +
   scale_y_continuous( name = "Projection on development axis [arbitrary units]"  ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)

```



```{r}
hs_projections <- projection_all %>%
  filter( include == "in", agebeginshock == 46, shockduration <=2, (abstime == 46.0 | abstime == 48.0 | abstime == 50.0 ) ) %>%
  select(-codeexp, -agebeginshock, -shockduration, dye, -abstime, -devprojection, -include ) %>%
  group_by(line, genotype, batch, experimentype) %>%
  summarize( hsprojection = mean(hsprojection) ) %>% ungroup() %>%
  spread( experimentype, hsprojection )

```

```{r}
p <- ggplot( ) + mytheme +
  geom_abline(slope = 1) +
  geom_point( data = hs_projections %>% filter( line == "PL"  ),
              aes( 
                    x = Dev,
                    y = HS,
                    colour = as.factor(genotype)
                ), alpha = 0.4, size = 5 )+
    geom_point( data = hs_projections %>% filter( line != "PL"  ),
              aes( 
                    x = Dev,
                    y = HS,
                    shape = as.factor(line)
                ), colour = "black", alpha = 1, size = 3 )+
   scale_x_continuous( name = "Projection on heat-shock response axis before heat shock"  ) +
   scale_y_continuous( name = "Projection on heat-shock response axis after 2 h"  ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)

```


```{r}
p <- ggplot( ) + mytheme +
    geom_abline(slope = 1) +
  geom_point( data = hs_projections %>% filter( line == "PL"  ),
              aes( 
                    x = HS,
                    y = Rec,
                    colour = as.factor(genotype)
                ), alpha = 0.4, size = 5 )+
    geom_point( data = hs_projections %>% filter( line != "PL"  ),
              aes( 
                    x = HS,
                    y = Rec,
                    shape = as.factor(line)
                ), colour = "black", alpha = 1, size = 3 )+
     scale_x_continuous( name = "Projection on heat-shock response axis after 2 h" ) +
   scale_y_continuous( name = "Projection on heat-shock response axis after 2 h recovery"  ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```

```{r}
p <- ggplot( ) + mytheme +
    geom_abline(slope = 1) +
  geom_point( data = hs_projections %>% filter( line == "PL"  ),
              aes( 
                    x = Dev,
                    y = Rec,
                    colour = as.factor(genotype)
                ), alpha = 0.4, size = 5 )+
    geom_point( data = hs_projections %>% filter( line != "PL"  ),
              aes( 
                    x = Dev,
                    y = Rec,
                    shape = as.factor(line)
                ), colour = "black", alpha = 1, size = 3 )+
   scale_x_continuous( name = "Projection on heat-shock response axis before heat shock"  ) +
   scale_y_continuous( name = "Projection on heat-shock response axis after 2 h recovery"  ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```


#Lifespan

```{r}
filelifespan <- "../../../Data/LifeSpan/Lifespan_GRAPPLE.txt"
lifespans <- read.csv( filelifespan, sep = "\t") %>%
  rename(genotype = Genotype) 

projection_lifespan <- inner_join(lifespans, hs_projections)

```


```{r}
p <- ggplot( ) + mytheme +
  geom_point( data = projection_lifespan %>% filter( line == "PL", Treatment == "ct"  ),
              aes( 
                    x = life.mean,
                    y = HS,
                    colour = as.factor(genotype)
                ), alpha = 0.4, size = 5 )+
    geom_point( data = projection_lifespan %>% filter( line != "PL" , Treatment == "ct" ),
              aes( 
                    x = life.mean,
                    y = Rec,
                    shape = as.factor(line)
                ), colour = "black", alpha = 1, size = 3 )+
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```

```{r}
p <- ggplot( ) + mytheme +
  geom_point( data = projection_lifespan %>% filter( line == "PL", Treatment == "ct"  ),
              aes( 
                    x = life.mean,
                    y = Rec,
                    colour = as.factor(genotype)
                ), alpha = 0.4, size = 5 )+
    geom_point( data = projection_lifespan %>% filter( line != "PL" , Treatment == "ct" ),
              aes( 
                    x = life.mean,
                    y = Rec,
                    shape = as.factor(line)
                ), colour = "black", alpha = 1, size = 3 )+
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```



```{r}
p <- ggplot( ) + mytheme +
    geom_point( data = projection_lifespan %>% filter( line == "NIL" , Treatment == "ct" ),
              aes( 
                    x = life.mean,
                    y = Rec,
                    shape = as.factor(line)
                ), colour = "black", alpha = 1, size = 3 )+
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```


```{r}
p <- ggplot( ) + mytheme +
    geom_point( data = projection_lifespan %>% filter( line == "RIL" , Treatment == "ct" ),
              aes( 
                    x = life.mean,
                    y = Rec,
                    shape = as.factor(line)
                ), colour = "black", alpha = 1, size = 3 )+
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```

rescale recovery by hs and dev

```{r}
p <- ggplot( ) + mytheme +
    geom_point( data = projection_lifespan %>% filter( line == "NIL" , Treatment == "ct" ),
              aes( 
                    x = life.mean,
                    y = (HS-Rec)/(HS-Dev),
                    shape = as.factor(line)
                ), colour = "black", alpha = 1, size = 3 )+
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```

```{r}
p <- ggplot( ) + mytheme +
    geom_point( data = projection_lifespan %>% filter( line == "RIL" , Treatment == "ct" ),
              aes( 
                    x = life.mean,
                    y = (HS-Rec)/(HS-Dev),
                    shape = as.factor(line)
                ), colour = "black", alpha = 1, size = 3 )+
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```


## Use RILS axis

```{r}

allprojection_lifespan <- inner_join(lifespans, projection_all)

```


```{r}
p <- ggplot( ) + mytheme +
 geom_point(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "ct", line != "PL") ,
              aes( 
                    x = life.mean,
                    y = dev_RILs_projection,
                    shape = as.factor(line),
                    colour = as.factor(line)
                ),   size = 3, alpha = 0.7) +
   geom_text(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "ct", line == "PL") ,
              aes( 
                    x = life.mean,
                    y = dev_RILs_projection,
                    label = as.factor(genotype)
                ), colour = 3,   size = 5, alpha = 0.7) +
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```


```{r}
p <- ggplot( ) + mytheme +
 geom_point(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "ct", line != "PL") ,
              aes( 
                    x = life.mean,
                    y = hs_RILs_projection,
                    shape = as.factor(line),
                    colour = as.factor(line)
                ),   size = 3, alpha = 0.7) +
   geom_text(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "ct", line == "PL") ,
              aes( 
                    x = life.mean,
                    y = hs_RILs_projection,
                    label = as.factor(genotype)
                ), colour = 3,   size = 5, alpha = 0.7) +
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```


```{r}
p <- ggplot( ) + mytheme +
 geom_point(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "ct", line != "PL") ,
              aes( 
                    x = life.mean,
                    y = rec_RILs_projection,
                    shape = as.factor(line),
                    colour = as.factor(line)
                ),   size = 3, alpha = 0.7) +
   geom_text(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "ct", line == "PL") ,
              aes( 
                    x = life.mean,
                    y = rec_RILs_projection,
                    label = as.factor(genotype)
                ), colour = 3,   size = 5, alpha = 0.7) +
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```


### Heat shock survival

```{r}
p <- ggplot( ) + mytheme +
 geom_point(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "hs", line != "PL") ,
              aes( 
                    x = life.mean,
                    y = dev_RILs_projection,
                    shape = as.factor(line),
                    colour = as.factor(line)
                ),   size = 3, alpha = 0.7) +
   geom_text(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "hs", line == "PL") ,
              aes( 
                    x = life.mean,
                    y = dev_RILs_projection,
                    label = as.factor(genotype)
                ), colour = 3,   size = 5, alpha = 0.7) +
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```


```{r}
p <- ggplot( ) + mytheme +
 geom_point(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "hs", line != "PL") ,
              aes( 
                    x = life.mean,
                    y = hs_RILs_projection,
                    shape = as.factor(line),
                    colour = as.factor(line)
                ),   size = 3, alpha = 0.7) +
   geom_text(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "hs", line == "PL") ,
              aes( 
                    x = life.mean,
                    y = hs_RILs_projection,
                    label = as.factor(genotype)
                ), colour = 3,   size = 5, alpha = 0.7) +
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```


```{r}
p <- ggplot( ) + mytheme +
 geom_point(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "hs", line != "PL") ,
              aes( 
                    x = life.mean,
                    y = rec_RILs_projection,
                    shape = as.factor(line),
                    colour = as.factor(line)
                ),   size = 3, alpha = 0.7) +
   geom_text(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "hs", line == "PL") ,
              aes( 
                    x = life.mean,
                    y = rec_RILs_projection,
                    label = as.factor(genotype)
                ), colour = 3,   size = 5, alpha = 0.7) +
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)
```


### Life mean vs Rec

```{r}

data_ls <- allprojection_lifespan %>%
  filter(abstime == 50 , experimentype == "Rec") %>%
  select(genotype, Treatment, line, life.mean, hs_RILs_projection) %>%
  spread(Treatment, life.mean) %>%
  rename( lifemean_ct =  ct, lifemean_hs = hs)

p <- ggplot( data_ls %>% filter(line != "PL")  ) + mytheme +
  aes( 
                    x = lifemean_hs/lifemean_ct,
                    y = hs_RILs_projection,
                    shape = as.factor(line),
                    colour = as.factor(line)
                ) +
  geom_point( size = 5, alpha = 0.7) +
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(name = "HS response - RILs axis"   ) +
  theme( legend.position = "bottom"  ) + facet_wrap(~line, scales = "free") 

show(p)

# RILS
data_RIls <- data_ls %>% filter(line == "RIL")
cor.test( data_RIls$lifemean_hs/data_RIls$lifemean_ct,  data_RIls$hs_RILs_projection  )

#NIL
data_NIls <- data_ls %>% filter(line == "NIL")
cor.test( data_NIls$lifemean_hs/data_NIls$lifemean_ct,  data_NIls$hs_RILs_projection  )


```


```{r}

data_ls <- allprojection_lifespan %>%
  filter(abstime == 48 , experimentype == "HS") %>%
  select(genotype, Treatment, line, life.mean, hs_RILs_projection) %>%
  spread(Treatment, life.mean) %>%
  rename( lifemean_ct =  ct, lifemean_hs = hs)

p <- ggplot( data_ls %>% filter(line != "PL")  ) + mytheme +
  aes( 
                    x = lifemean_hs/lifemean_ct,
                    y = hs_RILs_projection,
                    shape = as.factor(line),
                    colour = as.factor(line)
                ) +
  geom_point( size = 5, alpha = 0.7) +
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(name = "HS response - RILs axis"   ) +
  theme( legend.position = "bottom"  ) + facet_wrap(~line, scales = "free") 

show(p)

# RILS
data_RIls <- data_ls %>% filter(line == "RIL")
cor.test( data_RIls$lifemean_hs/data_RIls$lifemean_ct,  data_RIls$hs_RILs_projection  )

#NIL
data_NIls <- data_ls %>% filter(line == "NIL")
cor.test( data_NIls$lifemean_hs/data_NIls$lifemean_ct,  data_NIls$hs_RILs_projection  )


```


## Below not important

### Heat shock response correlation lifespan


```{r}
p <- ggplot( ) + mytheme +
 geom_point(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "hs", line == "RIL") ,
              aes( 
                    x = life.mean,
                    y = hs_RILs_projection
                ),   size = 3, alpha = 0.7) +
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)

data <- allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "hs", line == "RIL")

cor.test( data$life.mean,  data$hs_RILs_projection  )
```

```{r}
filelifespan_raw = "../../../Data/LifeSpan/Raw/Mark_files on RIL/LifespanRaw_Grapple.txt"
lifespan.data <- read.csv(file=filelifespan_raw,sep = "\t") %>% filter(Use_data != "CRAP")

#absolute number of dead worms per day
lifespan.data.2 <- cbind(lifespan.data[,c(1:9)],abs(data.matrix(lifespan.data[,-c(1:9)])-data.matrix(lifespan.data[,-c(1:8, ncol(lifespan.data))])))

#now I get the maximum of dead worms (the number of original worms per plate)
life.list <- mutate(lifespan.data,n=X51) %>%
             gather(key="day",value="dead",-c(Genotype:Comment),-n) %>%
             mutate(day=as.numeric(gsub("X","",day)),alive=n-dead,perc_alive=(n-dead)/n*100)
#And I merge this list with the deaths per day
life.list <- gather(lifespan.data.2,key="day",value="dead_per_day",-c(Genotype:Comment)) %>%
             mutate(day=as.numeric(gsub("X","",day))) %>%
             merge(life.list)

life.list <- life.list %>% rename( genotype = Genotype, line = Type ) 
  
  
  
  
```


```{r}
threshold_ls = 4

p <- ggplot(life.list %>% filter(genotype == "N2" | genotype == "CB4856"  ) %>% group_by(genotype,day, Treatment) %>%
              summarize( deadfrac = mean(dead_per_day/n) ) %>%
              ungroup()  ) + mytheme +
  geom_vline(xintercept = threshold_ls ) +
  aes(
    x = day,
    y = deadfrac,
    colour = as.factor(paste(Treatment,genotype))
  ) + geom_point() + geom_line()
show(p)

allprojection_lifespan <- inner_join(life.list %>% filter( day == threshold_ls), projection_all %>% filter(include == "in") %>%
                                       mutate( genotype = toupper(genotype)  ))
```


```{r}
p <- ggplot( ) + mytheme +
 geom_point(  data = allprojection_lifespan %>% filter(abstime == 48 , experimentype == "HS", Treatment == "hs", line == "RIL") ,
              aes( 
                    x = perc_alive,
                    y = hs_RILs_projection
                ),   size = 3, alpha = 0.7) +
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)

data <- allprojection_lifespan %>% filter(abstime == 48 , experimentype == "HS", Treatment == "hs", line == "RIL")

cor.test( data$perc_alive,  data$hs_RILs_projection  )

```


```{r}
p <- ggplot( ) + mytheme +
 geom_point(  data = allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "hs", line == "RIL") ,
              aes( 
                    x = perc_alive,
                    y = hs_RILs_projection
                ),   size = 5, alpha = 0.3) +
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous(   ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)

data <- allprojection_lifespan %>% filter(abstime == 50 , experimentype == "Rec", Treatment == "hs", line == "RIL")

cor.test( data$perc_alive,  data$hs_RILs_projection  )

```



```{r}
threshold_ls = 13

percalive <- life.list %>%
  select(-Comment, -Day_start,-Geno.use,  -dead_per_day,-n, -dead, -alive) %>%
  spread(Treatment, perc_alive) %>%
  rename( perc_alive_ct = ct, perc_alive_hs = hs )


p <- ggplot(  percalive %>% filter(line == "RIL", !is.na( perc_alive_hs)) %>%
                select(-genotype, -line, -Batch, -Use_data) %>%
                group_by( day ) %>%
                summarize_each(funs(mean)) %>% ungroup()
                ) + mytheme + geom_vline(xintercept = threshold_ls) +
                aes( 
                    y = perc_alive_hs/perc_alive_ct,
                    x = day
                ) + geom_point()  + geom_line() +
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous( ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 
show(p)

p <- ggplot(  percalive %>% filter(line == "RIL", !is.na( perc_alive_hs)) ) +
  mytheme + geom_vline(xintercept = threshold_ls) +
                aes( 
                    y = perc_alive_hs/perc_alive_ct,
                    x = day,
                    colour = as.factor(genotype)
                ) + geom_point()  + geom_line() +
   scale_x_continuous( name = "lifespan"  ) +
   scale_y_continuous( ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "none"  ) 
show(p)


allprojection_lifespan <- inner_join( percalive %>% filter( day == threshold_ls), projection_all %>% filter(include == "in") %>%
                                       mutate( genotype = toupper(genotype)  ))

proj_RILs_hs <- allprojection_lifespan %>%
  filter(line == "RIL") %>%
  select( genotype, perc_alive_hs, perc_alive_ct, experimentype, hs_RILs_projection ) %>%
  group_by(genotype, perc_alive_hs,perc_alive_ct, experimentype) %>% summarize( hsmean = mean(hs_RILs_projection) ) %>%
  ungroup() %>%
  spread( experimentype, hsmean)

p <- ggplot( ) + mytheme +
 geom_point(  data = proj_RILs_hs ,
              aes( 
                    y = perc_alive_hs/perc_alive_ct,
                    x = Rec
                ),   size = 5, alpha = 0.3) +
   scale_y_continuous( name = "lifespan"  ) +
   scale_x_continuous( ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 

show(p)

cor.test( proj_RILs_hs$perc_alive_hs / proj_RILs_hs$perc_alive_ct , proj_RILs_hs$Rec  )

```


#Physiological age vs lifespan et al

```{r}

phys_age <- projection_all %>% filter(line == "RIL", experimentype == "Dev") %>%
  select(genotype, devprojection)

HS_recomb <- projection_all %>% filter(line == "RIL", experimentype == "Dev") %>%
  select(genotype, hs_RILs_projection)  
  
physageHS <- inner_join( phys_age, HS_recomb )  
  
p <- ggplot( ) + mytheme +
 geom_point(  data = physageHS ,
              aes( 
                    y = hs_RILs_projection,
                    x = devprojection
                ),   size = 5, alpha = 0.3) +
   scale_y_continuous( name = "HS"  ) +
   scale_x_continuous( name = "Physiologial age" ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 
show(p)

cor.test( physageHS$devprojection, physageHS$hs_RILs_projection  )
```


```{r}

phys_age <- allprojection_lifespan %>% filter(line == "RIL", experimentype == "Dev", Treatment == "ct") %>%
  select(genotype, devprojection)

HS_recomb <- allprojection_lifespan  %>% filter(line == "RIL", experimentype == "Rec", Treatment == "ct") %>%
  select(genotype, hs_RILs_projection)  
  
physageHS <- inner_join( phys_age, HS_recomb )  

p <- ggplot( ) + mytheme +
 geom_point(  data = physageHS ,
              aes( 
                    y = hs_RILs_projection,
                    x = devprojection
                ),   size = 5, alpha = 0.3) +
   scale_y_continuous( name = "HS"  ) +
   scale_x_continuous( name = "Physiologial age" ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 
show(p)

cor.test( physageHS$devprojection, physageHS$hs_RILs_projection  )
```

```{r}
p <- ggplot( ) + mytheme +
 geom_point(  data = phys_age ,
              aes( 
                    y = life.mean,
                    x = devprojection
                ),   size = 5, alpha = 0.3) +
   scale_y_continuous( name = "devproj"  ) +
   scale_x_continuous( name = "life span" ) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 
show(p)

cor.test( physageHS$devprojection, physageHS$life.mean  )
```


HS RILs before, during, after

```{r}
Dev_HS <- allprojection_lifespan %>% filter(line == "RIL", experimentype == "Dev", Treatment == "ct") %>%
  select(genotype, hs_RILs_projection) %>% rename(Dev = hs_RILs_projection  )

HS_HS <- allprojection_lifespan  %>% filter(line == "RIL", experimentype == "HS", Treatment == "ct") %>%
  select(genotype, hs_RILs_projection)   %>% rename(HS = hs_RILs_projection  )

Rec_HS <- allprojection_lifespan  %>% filter(line == "RIL", experimentype == "Rec", Treatment == "ct") %>%
  select(genotype, hs_RILs_projection)     %>% rename(Rec = hs_RILs_projection  )

HS_exprm <- inner_join( inner_join( Dev_HS, HS_HS ), Rec_HS)

p <- ggplot( ) + mytheme +
 geom_point(  data = HS_exprm ,
              aes( 
                    y = HS,
                    x = Rec
                ),   size = 5, alpha = 0.3) +
  guides( colour = guide_legend( title = "treatment" ),
          shape = guide_legend( title = "treatment" )) +
  theme( legend.position = "bottom"  ) 
show(p)

cor.test( HS_exprm$HS, HS_exprm$Rec  )

```


## AA

```{r}
p <- ggplot(projection_all %>% filter( genotype == "N2",  experimentype == "Dev" ) ) + mytheme +
  aes(
    x = abstime,
    y = dev_RILs_projection,
    colour = as.factor(genotype)
  ) + geom_point(size = 4)
show(p)
```

